A search for high-mass black holes in data from the second LIGO observing run using a Bayesian ranking-statistic

### 2021-04-15 authors.tex
edits for v2

%------ affiliation shortcuts
\newcommand{\SPAno}{1}
\newcommand{\OzGravMonashno}{2}
\newcommand{\CITno}{3}
\newcommand{\MITno}{4}
\newcommand{\Kavlino}{5}

%--------------------------
\newcommand{\SPA}{School of Physics and Astronomy, Monash University, Clayton VIC 3800, Australia}
\newcommand{\OzGravMonash}{OzGrav: The ARC Centre of Excellence for Gravitational Wave Discovery, Clayton VIC 3800, Australia}
\newcommand{\MIT}{LIGO Laboratory, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
\newcommand{\Kavli}{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, \\ 77 Massachusetts Ave, Cambridge, MA 02139, USA}
\newcommand{\CIT}{LIGO Laboratory, California Institute of Technology, Pasadena, CA 91125, USA}
\author{
\parbox{\textwidth}{
A.~Vajpeyi$^{\SPAno,\OzGravMonashno}$, %ORCID:0000-0002-4146-1132
R.~Smith$^{\SPAno,\OzGravMonashno}$, %ORCID:0000-0001-8516-3324
E.~Thrane$^{\SPAno,\OzGravMonashno}$, %0000-0002-4418-3895
G.~Ashton$^{\SPAno,\OzGravMonashno}$, %ORCID:0000-0001-7288-2231 
J.~Kanner$^\CITno$, 
T.~Alford$^\CITno$, 
L.~Xiao$^\CITno$, %0000-0003-2703-449X
M.~Isi$^{\MITno,\Kavlino}$, %0000-0001-8040-9807
S.~Garza$^\CITno$, 
}\vspace{0.2cm}\\
$^1$\SPA\\
$^2$\OzGravMonash\\
$^3$\CIT\\
$^4$\MIT\\
$^5$\Kavli\\
}

>>>>

%------ affiliation shortcuts
\newcommand{\SPAno}{School of Physics and Astronomy, Monash University, Clayton VIC 3800, Australia}
\newcommand{\OzGravMonashno}{OzGrav: The ARC Centre of Excellence for Gravitational Wave Discovery, Clayton VIC 3800, Australia}
\newcommand{\CITno}{LIGO Laboratory, California Institute of Technology, Pasadena, CA 91125, USA}
\newcommand{\MITno}{LIGO Laboratory, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
\newcommand{\Kavlino}{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, 77 Massachusetts Ave, Cambridge, MA 02139, USA}

\author{A.~Vajpeyi}
\affiliation{\SPAno}
\affiliation{\OzGravMonashno}
\author{R.~Smith}
\affiliation{\SPAno}
\affiliation{\OzGravMonashno}
\author{E.~Thrane}
\affiliation{\SPAno}
\affiliation{\OzGravMonashno}
\author{G.~Ashton}
\affiliation{\SPAno}
\affiliation{\OzGravMonashno}
\author{T.~Alford}
\affiliation{\CITno}
\author{S.~Garza}
\affiliation{\CITno}
\author{M.~Isi}
\affiliation{\MITno}
\affiliation{\Kavlino}
\author{J.~Kanner}
\affiliation{\CITno}
\author{T.J.~Massinger}
\affiliation{\CITno}
\author{L.~Xiao}
\affiliation{\CITno}

% \affiliation[\OzGravMonashno]{}
% \affiliation[\MITno]}
% \affiliation[\Kavlino]{}
% \affiliation[\CITno]{}
